\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-08 intro.tex
intro cosmetic

In many settings, we may not have a physics-based model derived from
first principles, but may just have time-series data of the system
behavior. In such a setting, a data-driven model allows us to
generalize individual time-series behaviors through an abstract, PWA
relational model. There are several approaches in the literature to
perform data-driven modeling, system identification techniques that
learn dynamic models from data \cite{ljung1999system}, auto-regressive
models for forecasting \cite{wei1994time}, machine learning techniques
that learn static or dynamic models from data
\cite{narendra1990identification,lu2009linear}. However, in the second
step of our technique, \ie, symbolic analysis of the learned mode, we
need to have models that can be digested by existing symbolic tools,
which is harder to do with some of the aforementioned heavier
data-driven modeling methods. Hence, we use a lighter flavor of
data-driven modeling such as the one proposed for learning relational
models from data
\cite{zutshi2012timed,sankaranarayanan2011relational}. By learning
what is essentially a discrete-time dynamical system with PWA updates,
our technique permits us to use software analysis approaches such as
bounded model checking assisted by SMT and linear programming solvers.

The other perspective is when we have a model that is highly complex.
We note that the ultimate goal for our technique is to find violations
of safety properties in the {\em actual embedded control system}, and
not, per se, in the model. The aphorism attributed to mathematician
George E.P. Box is worth repeating,  ``all models are wrong, some
models are useful.'' Thus, we can sidestep analyzing a highly complex
model by approximating its behavior with a simpler relational model,
which in turn gives us promising tests to run on the actual system,
then our technique has intrinsic value.

>>>>

In many settings, we may not have a physics-based model derived from
first principles, but may just have time-series data of the system
behavior. In such a setting, a data-driven model allows us to
generalize individual time-series behaviors. But, there are several
approaches in the literature to perform data-driven modeling; e.g.,
system identification techniques that learn dynamic models from data
\cite{ljung1999system}, auto-regressive models for forecasting
\cite{wei1994time}, machine learning techniques that learn static or
dynamic models from data
\cite{narendra1990identification,lu2009linear}.  Why then do we need a
new modeling technique? The answer to this question lies in our goal
for the second step, \ie, symbolic analysis of the learned model. For
this step, we need to have models that can be digested by existing
symbolic tools, which is harder to do with some of the aforementioned
heavier data-driven modeling methods. Hence, we use a lighter flavor
of data-driven modeling such as the one proposed for learning
relational models from data
\cite{zutshi2012timed,sankaranarayanan2011relational}. By learning a
{\em PWA relational model}, \ie, essentially a PWA discrete-time
dynamical system, we can use software analysis approaches such as
bounded model checking assisted by SMT solvers and linear programming
solvers.

The other perspective for our technique is the context when we have an
effectively black-box model, \ie, a model that has features such as
nonlinearities, delays or look-up tables that make symbolic analysis
rather challenging.  We note that the ultimate goal for our technique
is to find violations of safety properties in the {\em actual embedded
control system}, and not, per se, in the model. The aphorism
attributed to mathematician George E.P. Box is quite apt for our
context, and bears worth repeating,  ``all models are wrong, some
models are useful.'' We can sidestep analyzing a highly complex model
by approximating its behavior with a simpler relational model, which
in turn can give us promising tests to run on the actual system. This
gives our technique intrinsic value as a debugging tool.
